Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-18 content/impl.tex
rcc instead of R

Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
Therefore, a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
is converted to an IFDS result as follows:
\begin{equation}\label{eq:transEqDef}
  \backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
\end{equation}
%\mtodo{Another change was that Ondrej defined $\backEq$ as $\lambda n.\{d\mid\rho(n)(d)=\top\}$
%and that he defined $\backEq$ related to the equivalence transformation.}
%\otodo{I don't understand this comment. What does it mean?}

@@

\begin{restatable}{lemma}{efficient}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient if the number of
  correlated-call receivers $R$ and the number of run-time types $T$ are considered constant.
\end{restatable}

From this lemma, we conclude that the correlated-calls analysis runs in time
$O(ED^3RT)$. In other words, the asymptotic cost of the added precision of
the correlated-calls analysis is increased by a factor of $O(RT)$ compared
to the original IFDS analysis.

>>>>

Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
Therefore, a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
is converted to an IFDS result as follows:
\begin{equation}\label{eq:transEqDef}
  \backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
\end{equation}

%\otodo{I don't understand this comment. What does it mean?}

@@

\begin{restatable}{lemma}{efficient}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient if the number of
  correlated-call receivers $\rcc$ and the number of run-time types $T$ are considered constant.
\end{restatable}

From this lemma, we conclude that the correlated-calls analysis runs in time
$O(ED^3\rcc T)$. In other words, the asymptotic cost of the added precision of
the correlated-calls analysis is increased by a factor of $O(\rcc T)$ compared
to the original IFDS analysis.
